Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-11-04 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

  geom_text(aes(y=c(-1,-1,-1), x=c(-2,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+

@@

  geom_text(data=dataG,aes(y=dataG$line, x=-2, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
  #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+
  theme_void() + 
  scale_y_reverse()+
  geom_segment(aes(y=max(dataG$line)+1, x=0, xend=1, yend=max(dataG$line)+1))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0,xend=0))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.25,xend=0.25))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.5,xend=0.5))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.75,xend=0.75))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=1,xend=1))+
  geom_text(aes(y=rep(max(dataG$line)+2,5),x=0:4/4, label=c(0.00,0.25,0.5,0.75,1.00)))+
  #geom_segment(data=dataG,aes(x=vlineloc, xend=vlineloc, y=0, yend=max(dataG$line)+1), linetype=3)+

>>>>

  geom_text(aes(y=c(-1,-1,-1), x=c(-1.3,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+

@@

  geom_text(data=dataG,aes(y=dataG$line, x=-1.3, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
  #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+
  theme_void() + 
  scale_y_reverse()+
  geom_segment(aes(y=max(dataG$line)+1, x=0, xend=1, yend=max(dataG$line)+1))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0,xend=0))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.25,xend=0.25))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.5,xend=0.5))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.75,xend=0.75))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=1,xend=1))+
  geom_text(aes(y=rep(max(dataG$line)+2,5),x=0:4/4, label=c(0.00,0.25,0.5,0.75,1.00)))+
  #geom_segment(data=dataG,aes(x=vlineloc, xend=vlineloc, y=0, yend=max(dataG$line)+1), linetype=3)+
